	INSTRUCTIONS FOR CAVALCADE O' CARD GAMES
 
 
 
General Information

  - A mouse is required to play all the games.
 
  - Clicking is done with the left button only.
  - Click the card you wish to affect.
  - Click to end pauses.
  - Most situations allow you to answer prompts by clicking on the 
actual word displayed.  This is how you choose what game to play,    
and the options for the game.  Another example is clicking on the    
word (K)nock, to knock in 31.

Prompts will be given for any other necessary actions.

			    Good Luck,
				&
			    Have Fun!


KLONDIKE SOLITAIRE

Object of game:
     Move all the cards into piles based on their suit and ordered   
     from ace to king.

Versions:

No-scoring: The goal of this game is to clear the board. There is no 
    scoring and you can flip the deck infinite number of times.

Scoring: In this version you can go through the deck 3 times and are 
    scored based on turning cards over or moving them to the piles.

Betting game: This game starts assuming you have paid 1 dollar per   
    card to play.  Every card you move to the side piles gets you 5  

    dollars. You can only go through the deck twice and must have at 
    least 52 dollars to continue to another game. 
 
RULES:
 
- Cards can be moved from one column to another if they are being
place below a card of the opposite color.  Cards must be placed in
descending order.
- Moving cards also means moving all the cards in the column that are
below it.
- Often moving cards will mean a face down card in fully exposed.
Flip this card by clicking it and now it is playable.
- Turn over cards from the source deck on the bottom by clicking on
it. 
You can move cards from off the top of the discard deck.
- Aces are important.  The goal is to move all the cards to the four
empty spaces on the left.  The piles must be started with an ace and
continued in ascending order of the same suit.
- As cards become available move them to the left side piles.
- There are seven columns of cards in the game. As one becomes empty
only kings can be put at the top of the screen.

CONTROLS:
- Click the cards you want to flip over.
- To move a card first click the card and then click the location
where you want it to go.
- With a mouse you can click the first card then release over the
destination.
- To send a card to the left hand piles, you need just to double
click (except for kings).
- If there is an empty row on the top, double clicking a king will
move it there (except from the discard deck). 



GOLF SOLITAIRE

Object of game:

To move all the cards from the top play area into the discard deck.

Rules:

- Cards can only be moved to the discard deck if their face value is
  one above or one below the card currently on top of the discard deck.
- No cards can be placed on a king on top of the discard deck.
- If there are no cards to move to the discard pile, click on the
  source deck to draw a new card.

Controls:

- Single click on a card which you want to put on the discard pile.
- Single click the source deck to draw a card.


KING'S THRONES

Object of game:

To move all the kings from the play area onto the tops of the four decks
on the far left.

Rules:

- Aces are low cards and do not wrap around to king.
- One king must be on top of each of the 4 left side piles to win.
- You can only move cards around if they are one value above or below
  the card onto which you want to move them.
- Cards can be place on the left side piles in ascending or descending 
  order.
- The play area consists of 12 columns of 4 cards each. No more than
  four cards can be in a column, and once a column is empty nothing can
  be placed in it's spot.
- Cards can be moved from the bottom of each these columns to other
  columns or to the piles.

Controls:

- Click and drag cards to their new location.


STREETS AND ALLIES

Object of game:

To move all the cards to the center piles in ascending order of the
same suit starting with the aces.

Rules:

- Aces can only be moved to the center spaces.
- Cards can be moved from the end of one row to the end of another if 
  it is one value above or below the card it is going onto.
- Each row can have a maximum of 13 cards in it.

Controls:

- Click and drag cards to their new location.



MATCHING GAME

Object of the Game:

One player: match all the cards in fewest turns possible.
Two player: find more cards than your opponent.

RULES:

- Turn over pairs in hope of matching their values.
- In the two player game turns alternate, except if a player finds a
pair.
- Scores are kept in the two player version.

CONTROLS:
- point and click desired cards.


CRAZY 8'S

Object of the game:

     To get rid of all your cards before the computer gets rid of    
     it's.

RULES:

- The player and the computer takes turns placing cards onto the
discard pile as long as the cards put down match the suit of the card
currently face up on the pile.
- The suit can be changed in two conditions - 
     1) if a card is laid down with the same value as the card       
	currently on the discard pile then the active suit changes to
	that of the new card.
     2) if an 8 is played then the player can pick any suit to be the
	active suit.

- Generally the player and the computer alternate turns except when a
either plays a jack.  In this situation the other misses a turn.
- When either the player or the computer lays down a two the other
player must pick up two cards from the source deck.  If a two is
played on top of that two the then next player must pick up four
cards.  This continues to a maximum of picking up 8 cards.
     ie. 2,4,6,8,0,2,4,6,etc.
 
- The queen of spades requires that the other player pick up 5
cards.
- When the source deck runs out of cards then the decks are flipped
and shuffled and play continues.
- When you have no cards you can play, take one off the discard deck.

CONTROLS: 

- Click cards to discard them.
- Single click the source deck to draw cards.
- To change the suit after playing an 8 click the suit
displayed within the box.


31

Object of the game:

     To play 15 hands against the computer and have the most points  
     at the end.

RULES:

- Each player can possess only 3 cards at one time.  The goal for
each hand is to have more points than the other player.

- Points are calculated for only cards of the same suit.
- Aces count for eleven making the highest possible hand 31.
- Three of a kind counts as 30.5.

- During play players pick a card from either the discard pile or the
source pile and then click the card they want to dispose of.  This is
done so that the players only have three cards in hand at a time.
- If you think you have a winning hand hit 'K' to knock which gives
the computer one more draw before the hand finishes and the best
hand collects points.
- Points are calculated by the points contained in the winning hand
plus the difference between the winner and the losing hand.
- After the computer (k)nocks you have one more draw.

CONTROLS:

- Your hand is the three cards at the bottom of the screen. The space
above them is where the currently drawn card is placed.
- Click any of these locations to discard the unwanted card.  If you
discard a card currently in your hand the card drawn will move down
and replace it in the hand.
- To draw a card click on the source or discard deck.
- Click on the word (K)nock to knock.


52 PICKUP

Object of the game:

One Player: To accumulate the most points possible by picking cards  
	    to create sets, straights, or straight flushes.
Two Players: Same as for one player except now you must also attempt  
	    to stop your opponent from winning by using sneaky and   
	    underhanded moves.

RULES:

- Only the cards that are completely visible on the top of the pile
can be moved.
- A set (cards with the same value), straight, straight flush or a
combination of these makes up a trick.
- All straights & flushes must be played in descending order with
Aces able to be played as both high & low card.
       ex: 4,3,3,2,A,K,K,Q,...
- Each of the two tricks are independent and do not interact except
to add their points together in a one-player game. Tricks are
intended to build themselves on what the other trick has unburied.

CONTROLS:

- Click on the cards to move.

- With a mouse:
     To call a trick click on the highlighted trick box and to       
     switch between tricks click on the non-highlighted trick box.


BLACKJACK

Object of the game: Try to maximize net earnings.

RULES:

- The game is set up as a casino with a dealer and a maximum of 3
players.
- The game first asks for bets to be placed and this is done by
entering the appropriate amount (maximum bet 1 hundred dollars).
- You cannot change your bet as numbers are entered. Bets over $100
are changed to $100.
- Each player bets in turn and then the dealer deals two cards each.
- Each player in turn handles their cards.
- The point is for the value of your hand to be as close to 21 as
possible without going over.

- After each player has gone the dealer deals itself and winnings are
paid out.
- If the values for the first two cards are equal to 10 or 11 the
player is prompted to whether or not to double down.
- A card will be laid face down and on your pile and your bet will
double.
- After this the next player goes.
- If the values for the first two cards are equal to eachother the
player is prompted if they want to split.  If they respond 'y' the
cards become the first cards of two separate and independent hands
which are immediately played.
- Players can doubledown on either of these but cannot further split.
- If the first two cards dealt are a ten value and an ace this is a
blackjack and you do not play the cards but receive 1.5 times your
bet at the end of the deal.
- Aces are assumed to be valued at 11 except if this leads to over
21, then they are counted as 1.

CONTROLS:

- Bet by clicking on the dollar amounts displayed.
     ie. 100's 10's 1's.
- End the bet by clicking on the word 'end'.
- Prompts which appear can be answered by clicking on the letter
shown or by using the keyboard.


SCOREBOARDS:

Scoreboards are kept for solitaire (scoring), one player matching
game, 31 and 52 pickup.

They can be viewed by selecting it in the menu screen or the option
screen.

Games with scoreboards available will be displayed.  Make your
selection.

Once viewed click space bar or click mouse to end.
To reset scoreboards:
     Once in the scoreboard menu after selecting scoreboards, press  
     control 'n' the press the game you want to reset.  Press escape 
     if you change your mind. No prompts are shown for this.

To Enter Name:

Type name in normally at space indicated by arrow, up to eight
letters.

You can backspace to fix errors.

Press enter win done, then click.


OPTIONS SCREENS:

These two screens allows you to change various environmental
conditions.

Press Home (or click Home icon) to leave screen.

PAGE 1:

The games play with two different sizes of cards. You can change what
card back is used with each deck (large and small) for six options
for each.

Without a mouse:

A grey square and a yellow square surround current card backs.  The
yellow square indicates that it is currently active.  This means that
moving the arrows left and right will change what card back is used
for that deck.  To move to the other deck use up or down arrow key,
whatever is appropriate.

To change the screen color hit the number of the color you want.

Instructions and scoreboards can also be called from the first page
of the options screen.

With a mouse:

Click on what ever you want.

PAGE 2:

Without a mouse:

Move box up and down options with arrow keys. Hit left or right arrow
keys to turn first three options on or off.

Move box to the music selection area to select which tunes to play
for which part of the game.  To select the tune for where the box is,
press the number of the tune indicatedon the left.  Enter 0 if you
want no tune for that part.

With a mouse:

Click the words 'on' or 'off' for your choices. To change music
selections, click on the game section the use the keyboard to enter
the new tune to play for that part.

GENERAL NOTES:

- The music for the winner screen is not changeable but can be shut
off by turning of the sound.
- Options screen can be entered in any game. There are some
restrictions within each game when the options can be chosen.


NOTES

When running this program from inside TSR's it may be necessary to 
allocated more memory to it than default settings.  For best results
try to give this program all the memory it can get.  The primary
symptom which may indicate a need to do this is poor mouse operation
such as not registering all the clicks sufficiently.

SCREENSAVER: If this game is left idle for more than approximately
2 minutes, a screen saver will come on.  This screen saver does not
come on if you are expected to reply to a prompt.  The small circle
in the bottom right corner of the screen indicates that the screen
saver timer is activated.

Although all files must be included unaltered for distribution, the
program can run successfully with only the .EXE and the SOURCE*.DAT
files.  Depending on what files are missing use of online
instructions, and scoreboards may be inhibited.  If you suspect
any files that are not .EXE or .DAT of being corrupted, try
removing the files from the game's directory (be sure to back
them up) and running the program.  To rebuild proper data for the
*.CGS files reset all the scoreboards as describe above.

ABOUT THIS SHAREWARE GAME:

The game is marketed in two formats.  One shareware version (2.5s)
and one non-shareware version (2.5r).  The shareware version may
be freely distributed or sold for no more than a moderate
duplication fee. After a reasonable trial period you are
encouraged to register your copy and obtain the full non-shareware
program.  This non-shareware version (the registered version) is
copyright by the author who retains all rights to the program.
The registered version will contain all nine games and is not to
be further distributed by anyone without the written consent of
the author.  Please do not distribute the registered version.
Distribution of this program must contain all the following
files in their entirety and unaltered:

	CAVAL25S.EXE      DATA2.CGS
	SOURCE0.DAT       DATA4.CGS
	SOURCE1.DAT       DATA5.CGS
	SOURCE2.DAT       
	SOURCE3.DAT       VENDOR.DOC
	SOURCE4.DAT       INSTRUCT.TEX
	SOURCE5.DAT       FILE_ID.DIZ
	SOURCE6.DAT
	SOURCE7.DAT
	DATA1.CGS

IF YOU ARE A VENDOR PLEASE READ THE VENDOR.DOC BEFORE DISTRIBUTING.  
 

__________________________________________________________________
